5'CutSiteAnalysisDataGeneration

### 2022-07-28 R/5'CutSiteAnalysisDataGeneration.rmd
Preliminary commit

```{r compute_and_write_sequence_frequencies}
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CAC","CAG","CAT"), "CAB", humanReadMinMax)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", drosophilaReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("TCAGTC","TCAGTT"), "TCAGTY", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("TCAGTC","TCAGTT"), "TCAGTY", drosophilaReadMinMax)
```

>>>>

```{r compute_and_write_sequence_frequencies_OLD}
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CAC","CAG","CAT"), "CAB", humanReadMinMax)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", drosophilaReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("TCAGTC","TCAGTT"), "TCAGTY", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("TCAGTC","TCAGTT"), "TCAGTY", drosophilaReadMinMax)
```

```{r compute_and_write_sequence_frequencies}
HYV = c("ACA","ACC","ACG","ATA","ATC","ATG",
        "CCA","CCC","CCG","CTA","CTC","CTG",
        "TCA","TCC","TCG","TTA","TTC","TTG")
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYV, "HYV", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", drosophilaReadMinMax)

```
